Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-27 paper/snakemajoranas.tex
write the author contributions in active voice

\section{Author contributions}
The idea of the zigzag geometry was authored by T.L.
The code was written by B.N. and extended by T.L.
The writing of the manuscript was performed by B.N. with input of T.L. and A.A.
The analysis of the results and planning of the project were performed by all authors.

>>>>

\section{Author contributions}
T.L authored the idea of the zigzag geometry.
B.N. wrote the code and it was extended by T.L.
B.N. performed the writing of the manuscript with input of T.L. and A.A.
All authors performed the analysis of the results and planning of the project.
